Experience Report: Haskell in Computational Biology

### 2012-06-27 mrfy_experience_report.tex
I've restored block style.  It's not enough for our paper to appear in the proceedings; for it to have an impact, people have to read it. Well worth the additional two column inches.
A paragraph about The QuickCheck Experience (tm).

\documentclass[nonatbib]{sigplanconf}

@@

>>>>

\documentclass[nonatbib,blockstyle,times]{sigplanconf}
  % at 9pt anything but block style is unreadable

@@

This was a practice that the junior members of our team did not follow, and
they sorely regret it.
We speculate that one reason why we didn't follow this practice was a poor 
understanding of the \texttt{Arbitrary} type class.
Namely, a lot of the examples we had seen using QuickCheck focused 
predominantly on writing and testing properties with data types that already 
implemented \texttt{Arbitrary}.
We recall a smattering about \texttt{Arbitrary}, but we were still too baffled 
by the \texttt{Gen} monad to truly grasp its importance in using QuickCheck.
When it finally came time to use QuickCheck, we were overwhelmed by the amount 
of work that had to be done to write and test implementations of 
\texttt{Arbitrary} for each of our data types.
